---
title: "Some options to implement guidance to reduce SARS-CoV-2 transmission"
date: "`r format(Sys.time(), '%d-%B-%Y')`"
mainfont: Verdana
output:
  word_document:
    reference_docx: "customrep.docx"
header-includes: \usepackage{fancyhdr}
---
\addtolength{\headheight}{1.0cm} 
\pagestyle{fancyplain} 
\chead{\includegraphics[height=2cm]{www/image1.jpg}}
\renewcommand{\headrulewidth}{0pt} 

There is a wide set of guidance on reducing SARS-CoV-2 transmission that should be used to explore options for implementing that guidance.

`r if(length(c(input$rank_list_2a,input$rank_list_4a,input$rank_list_6a))>0){paste("Risk:",input$risk1,sep=" ")}`

```{r echo = FALSE,  warning=FALSE}
library(knitr)
if(length(c(input$rank_list_2a,input$rank_list_4a,input$rank_list_6a))>0){
  kable(x=c(input$rank_list_2a,input$rank_list_4a,input$rank_list_6a), col.names = '',row.names = TRUE)}
```


`r if(length(c(input$rank_list_2b,input$rank_list_4b,input$rank_list_6b))>0){paste("Risk:",input$risk2,sep=" ")}`

```{r echo = FALSE, linewidth=60,warning=FALSE}
library(knitr)
if(length(c(input$rank_list_2b,input$rank_list_4b,input$rank_list_6b))>0){
kable(x=c(input$rank_list_2b,input$rank_list_4b,input$rank_list_6b), col.names = '',row.names = TRUE)
}
```

`r if(length(c(input$rank_list_2c,input$rank_list_4c,input$rank_list_6c))>0){paste("Risk:",input$risk3,sep=" ")}`

```{r echo = FALSE, linewidth=60, warning=FALSE}
library(knitr)
if(length(c(input$rank_list_2c,input$rank_list_4c,input$rank_list_6c))>0){
kable(x=c(input$rank_list_2c,input$rank_list_4c,input$rank_list_6c), col.names = '',row.names = TRUE)
}
```

This is derived from the [ShinyApp](https://alecchristie888.shinyapps.io/Covid_19_options) from the list of options [https://covid-19.biorisc.com](https://covid-19.biorisc.com) from a solution scan of the means to reduce SARS-CoV-2 transmission (Paper preprint: [https://osf.io/ca5rh/file](https://osf.io/ca5rh/file)).